%!TEX root = ../cv.tex
% main-file: ../main.tex
\documentclass[letter,10pt]{article}
\usepackage{cv}
\begin{document}

\subsection{{Teaching / Lab Assistant \hfill Jan 2022 --- Present (remote)}}
\subtext{\href{https://lensky-kray.ru/}{Sakha Junior Science Academy (SJSA)} \hfill Yakutsk, Russia}
\begin{zitemize}
\item Controlling SJSA ground station as a licensed radio operator, providing technical support.
\item Supervising high school students practicing satellite communications (\href{https://www.yakutia.kp.ru/daily/27434.5/4635501/}{news report in Russian}).
\item Served as a research advisor for a student who won a silver medal at the Taiwan International Science Fair 2024.
\item Helped to organize an international aerospace engineering school (\href{https://www.luac.edu.hk/vineyard-2023-2024-issue-3/}{see page 2 and 27}) for high school students from Hong Kong; worked remotely as electronics engineering TA.
\item Performed duties of flight director \& RF communications engineer for a high altitude balloon launch (\href{https://news.tvb.com/tc/local/6643e73a27f15d1b8cd1baf6}{news report}).
\item Assisted colleagues from Siberian State Aerospace University, Krasnoyarsk, in receiving telemetry from their CubeSat (\href{https://db.satnogs.org/satellite/EUTM-6475-4739-7036-7152}{ReshUCube, NORAD 53382}) via SJSA ground station.
\end{zitemize}

\subsection{{Lead Engineer / SAKHACUBE-CHOLBON CubeSat \hfill Jul 2021 --- Present (remote)}}
\subtext{\href{https://www.yksa.space}{Sakha Aerospace Systems, LLC} \hfill Yakutsk, Russia}
\begin{zitemize}
\item Serving as the lead engineer \href{https://www.yksa.space/projects/sakhacube-cholbon}{for a CubeSat project}; scheduled for launch in \textbf{Q4 2024}.
\item Developing and maintaining web service infrastructure, see Projects section for details.
\item Developing flight software for CubeSat Payloads, C / Atmel AVR.
\item Preparing technical documents, reports and specifications with IEEE standards compliance.
\item Designed CubeSat payload flight electronics -- \href{https://yktaero.space/projects/item/ykts-pl-edu16-sptx}{YKTS-PL-EDU/16 MCU Cluster Module}.
\end{zitemize}

\subsection{{Intern / Junior Software Engineer \hfill Mar 2021 --- Jun 2021}}
\subtext{\href{https://itykt.ru}{<<Sever>> Information Security Center, LLC} \hfill Yakutsk, Russia}
\begin{zitemize}
\item Developed an internal quote generation tool with automated supplier data import, Flask/Python.
\item Practiced network engineering, VMware ESXi management.
\end{zitemize}

\subsection{{Intern / Electronics Engineer, Lab Assistant \hfill Jun 2019 --- Nov 2020}}
\subtext{\href{https://ikfia.ysn.ru/en/}{Yu.~G.~Shafer Institute of Cosmophysical Research and Aeronomy} \hfill Yakutsk, Russia}
\begin{zitemize}
\item Assembled PCBs for reindeer tracking collars, studied electronics engineering.
\item Studied satellite \& radio communication basics.
\item Taken high-energy particle physics courses.
\end{zitemize}
\end{document}
