\documentclass[letter,11pt]{article}
\usepackage{cv}
\begin{document}
    \begin{justify}
        \begin{enumerate}
            \item As I mentioned in my essay, I have an official, government-issued certificate of qualification in spacecraft design. I got it during my internship at Siberian State Aerospace University in Krasnoyarsk.

            \item I had an internship at V.P.Glushko JSC Energomash, the largest rocket engine manufacturer in Russia.
            
            \item I have a category II amateur radio license (US Amateur Extra Class equivalent), and my callsign is R0QAV.
            
            \item I have a gas-powered bicycle. We call it ''Дырчик'' and we built it with my friends during 2020 summer break using spare parts of a soviet moped ''Riga-16''.
            
            \item To build a payload for Sakha Junior Science Academy's CubeSat, we have founded a startup company called Sakha Aerospace Systems, LLC. Currently, only me and my friends work there, but we recently got a government grant, and we are going to expand. The word ''Sakha'' is what Yakut people call themselves; therefore, the name <<Sakha Aerospace Systems>> means <<Aerospace Systems from Yakutia>>. You can visit our website (in Russian for now, working on a translation): \url{https://yktaero.space}
            
            \item I am a finalist of the SOLAR (Space-Oriented Learning for Americans and Russians) exchange program. Due to travel restrictions, however, the program was closed, and I never visited the US.
            
            \item I love self-hosting stuff, and I have a home lab. Since elementary school, I always was the guy who had a game server for every occasion. I still host a Minecraft server - join me at \url{mc.thepetrovich.ru:25565} (JK, but if you really want it...). Some of my other services include yktaero.space website, Gitlab, Nextcloud, Onlyoffice, Jitsi Meet, and all of this is running on my VMWare ESXi cluster.
        \end{enumerate}
    \end{justify}
\end{document}




