\documentclass[letter,10pt]{article}
\usepackage{cv}
\begin{document}

\subsection{{Sakha Aerospace Systems Ground Station Network \hfill In development}}
\subtext{Link: \url{https://gsn.yktaero.space} \hfill Stack: Django, Jinja2, Django REST, Django Channels}
\begin{zitemize}
\item Provides a public API to query satellite ground station status.
\item Visualizes ground station operation by displaying antenna position and satellite passes.
\item Receives real-time satellite telemetry data and forwards it to clients.
\item Generates satellite pass schedule and manages ground station tracking.
\item (Planned) Provides a public satellite imagery repository using ground stations.
\item (Planned) Stores past telemetry packets and allows to obtain historic satellite data.
\end{zitemize}

\subsection{{YktSat EDU/16 Payload Module \hfill In development}}
\subtext{Link: \url{https://yktaero.space/projects/item/ykts-pl-edu16-sptx} \hfill Stack: KiCad, C/C++, Doxygen}
\begin{zitemize}
\item Conforms with PC/104, CubeSat, and Sputnix ICD specifications.
\item 4-Layer modular PCB, designed from scratch in KiCad.
\item Modular firmware written in C \& AVR assembly, unit tests with CppUTest, CI/CD supported.
\item Single makefile, firmware built and tested with self-hosted GitLab.
\end{zitemize}

\subsection{{Sakha Aerospace Systems Datasheet website \hfill Operational}}
\subtext{Link: \url{https://docs.yktaero.space} \hfill Stack: Django, Jinja2, Django REST}
\begin{zitemize}
\item Provides users with a list of all published technical documents.
\item Search, filtering, reordering supported.
\item Stores and displays revision history for all documents, provides file downloads for every revision.
\item Allows creating new documents and uploading files via administration panel.
\item (Planned) GitLab CI integration for {\LaTeX} documents with automated publishing.
\end{zitemize}

\subsection{{Ground Station Controller - stationctl \hfill Operational}}
\subtext{Internal tool \hfill Stack: Python, GnuRadio, Skyfield}
\begin{zitemize}
\item Estimates satellite position in real time using orbital elements.
\item Automatically adjusts radio link parameters (data rate, carrier frequency with Doppler shift, etc.).
\item Aims antenna rotator to the satellite position.
\item Production deployment \& usage in Sakha Junior Science Academy.
\end{zitemize}

\subsection{{Sakha Aerospace Systems website \hfill Operational}}
\subtext{Link: \url{https://yktaero.space} \hfill Stack: Python, Django, Jinja2}
\begin{zitemize}
\item Simple landing page, blog and project overview.
\item No front end frameworks, blazing fast (95+ PageSpeed).
\item CI/CD with self-hosted GitLab.
\end{zitemize}

\subsection{{Sakha Aerospace Systems development infrastructure \hfill Operational}}
\subtext{Link: \url{https://status.yktaero.space} \hfill Stack: VMware ESXi, pfSense, nginx}
\begin{zitemize}
\item Various services for team collaboration: Nextcloud, Gitlab, Onlyoffice, Inventree.
\item Simple status reporting with GitHub Pages, internal monitoring with Zabbix.
\item Single Sign-On for all services using self-hosted Authentik, migration to Keycloak is planned.
\item Fully self-hosted \& virtualized, proper network isolation with VLANs, secure remote access with OpenVPN.
\item Server uses enterprise-grade hardware.
\end{zitemize}

\subsection{{YktSat PL-RTOS kernel \hfill Production usage}}
\subtext{Internal tool \hfill Stack: C/C++, Doxygen}
\begin{zitemize}
\item Fully-featured Real Time Operating System (RTOS) kernel for MCUs.
\item Currently supports AVR ATmega128 \& ATmega2560, ARM Cortex-M4 support planned.
\item Experimental task child--parent relationship with batch task operations.
\item Mutex priority inheritance and FIFO locking.
\item Built-in heap manager with allocation tracking and double free protection.
\item Unit tests with CppUTest, Doxygen for documentation.
\item Used in YktSat EDU/16 Payload Module firmware.
\end{zitemize}

\subsection{{UEFI mods \hfill Production usage}}
\subtext{Personal project \hfill Stack: TianoCore EDK II, UEFITool}
\begin{zitemize}
\item DXE module with secret notes, activated with key combo, written in C with EDK II.
\item Patched personal workstation EFI image with my custom DXE module, also added support for NVMe boot.
\item Customized logos, UI images, backgrounds and DMI information; updated bult-in DXE drivers to latest versions. 
\item Flashed modded images into hardware, haven't bricked my PC.
\end{zitemize}
\end{document}